---
title: "Main_SRBC"
author: "Pranita Patil, Emily Wefelmeyer, Sridhar Ravula"
date: "November 27, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Load libraries
```{r}
if (!require('RCurl')) install.packages('RCurl', quiet=TRUE)
require(Rcurl)

if (!require('readxl')) install.packages('readxl', quiet=TRUE)
library(readxl)

if (!require('dplyr')) install.packages('dplyr', quiet=TRUE)
library(dplyr)

if (!require('Hmisc')) install.packages('Hmisc', quiet=TRUE)
library(Hmisc)

if (!require("stringr")) install.packages("stringr", quiet = TRUE)
library(stringr)

if (!require("lubridate")) install.packages("lubridate", quiet = TRUE)
library(lubridate)

if (!require("rstudioapi")) install.packages("rstudioapi", quiet = TRUE)
library(rstudioapi) 
current_path <- getActiveDocumentContext()$path 
setwd(dirname(current_path ))

```

##Import Excel files from Git
###Function
```{r}
importGitHub <- function(url, skip){
  df <- read.csv(text = getURL(url),
                 skip = skip)
  
  return(df)
}
```

###Chemistry Data 
####Load chemistry data
```{r}
source("import_chemistry.R")
chemistry2 <- import_chemistry()
```

###Fish Data 
####Load Fish data
```{r}
source("import_fish.R")
fish <- import_fish()
fishCounts <- fish[[1]]
fishCounts2 <- fish[[2]]
```

###Macro Counts
```{r}
source("import_macro.R")
macroCounts2 <- import_macro()
```

###Attribute data for each site
###Water Quality Measures for entire system
```{r}
source("import_attribute_micro.R")
attribute_micro <- import_attribute_micro()
attributes <- attribute_micro[[1]]
micro <- attribute_micro[[2]]
```

### Calculate fish metrics
```{r}
source("Metrics_fish.R")
fishCounts2 <- Metrics_fish(fishCounts, fishCounts2)
```

###Average high frequency data
```{r}
DateTime2 = seq.POSIXt(min(chemistry2$DateTime), max(chemistry2$DateTime), by='4 hour')

DateTime <- as.data.frame(seq(ISOdatetime(1983, 8, 10, 0, 0, 0), 
                ISOdatetime(2018, 10, 1, 0, 0, 0),
                by = "4 hours"))
colnames(DateTime) = "DateTime"

StationID <- unique(chemistry2$StationID)
StationID <- as.numeric(StationID)
nStations = as.numeric(length(StationID))

hourseq = seq.POSIXt(min(micro$DateTime), max(micro$DateTime), by='4 hour')
microt<- micro %>%
   group_by(DateTime = cut(DateTime, breaks=hourseq)) %>%
   summarise_all(mean)  %>% drop_na(DateTime)

microt$DateTime <- as.POSIXct(microt$DateTime, 
                             format = "%Y-%m-%d %H:%M")


micro2 <- merge(DateTime, 
                  microt, 
                  by.x = "DateTime", 
                  by.y = "DateTime", 
                  all.x = TRUE)
rm(hourseq,microt)


hourseq = seq.POSIXt(min(chemistry2$DateTime), max(chemistry2$DateTime), by='4 hour')
chemistry2t<- chemistry2 %>%
   group_by(StationID, StationName,DateTime = cut(DateTime, breaks=hourseq)) %>%
   summarise_all(mean)  %>% drop_na(DateTime)

chemistry2t$DateTime <- as.POSIXct(chemistry2t$DateTime, 
                             format = "%Y-%m-%d %H:%M")
chemistry3 <- merge(DateTime,
                    chemistry2t,
                    by.x = "DateTime",
                    by.y = "DateTime")

rm(hourseq,chemistry2t, DateTime, micro, chemistry2, DateTime2)
```


### Combine all Data frames
```{r}
###Combine chemistry, fish count & macro count data
#Create initial data frame from varous pieces
chem <- subset(chemistry3, StationID == StationID[1])
fish <- subset(fishCounts2, StationID == StationID[1])
macro <- subset(macroCounts2, Station_ID == StationID[1])

#Combine fish & macro counts
temp <- merge(fish,
              macro,
              by = "DateTime",
              all = TRUE)

#Clean to have unified station ID
temp$StationID <- rep(StationID[1], times = nrow(temp))
temp$Station_ID.x <- NULL
temp$Station_ID.y <- NULL

#Add in chemistry
temp <- merge(chem,
              temp,
              by = "DateTime",
              all.x = TRUE,
              all.y = TRUE)

#Clean to have unified station ID
temp$StationID <- rep(StationID[1], times = nrow(temp))
temp$StationID.x <- NULL
temp$StationID.y <- NULL

#Create initial data frame
data <- temp
rm(temp)

#Combine rest of the data frames
for(station in StationID[2:nStations]) {
  chem <- subset(chemistry3, StationID == station)
  fish <- subset(fishCounts2, StationID == station)
  macro <- subset(macroCounts2, StationID == station)
  
  #Combine fish & macro counts
  temp <- merge(fish,
                macro,
                by = "DateTime",
                all = TRUE)
  
  #Clean to have unified station ID
  temp$StationID <- rep(station, times = nrow(temp))
  temp$Station_ID.x <- NULL
  temp$Station_ID.y <- NULL

  #Add chemistry data
  temp <- merge(chem,
                temp,
                by = "DateTime",
                all.x = TRUE,
                all.y = TRUE)
  
  #Clean to have unified station ID
  temp$StationID <- rep(station, times = nrow(temp))
  temp$StationID.x <- NULL
  temp$StationID.y <- NULL

  #Add station's data to the full data set
  ifelse(nrow(temp) > 0, 
    (data[(nrow(data)+1):(nrow(data) + nrow(temp)),] <- temp[1:nrow(temp),]),
    data <- data)
}

#rename data frame
fishMacroCountsWithChem <- data
rm(chem, data, fish, macro, nStations, station, temp)

##Combine micro df with fish & macro counts df
chemFishMacroMicro <- merge(micro2,
                        fishMacroCountsWithChem,
                        by = "DateTime",
                        all = TRUE)

##Add attributes
allData <- merge(attributes,
                 chemFishMacroMicro,
                 by.x = "Station.ID",
                 by.y = "StationID",
                 all.y = TRUE)

summary(allData)


##Remove unneed variables
rm(StationID)
```

### Add communtity metrics from R package
```{r}
source("community_metrics.R")
addData <- community_metrics()
```


### Calculate correlations
```{r}
source("Corr_SRBC.R")
corr_results <- Corr_SRBC()
```

### Calculate PCA
```{r}
source("PCA_SRBC.R")
PCA_results <- PCA_SRBC()
```

### Build GLM
```{r}
source("GLM_SRBC.R")
GLM_results <- GLM_SRBC()
```

### Build GAM
```{r}
source("GAM_SRBC.R")
GAM_results <- GAM_SRBC()
```

### combining GLM & GAM 
```{r}
source("GLM_GAM_SRBC.R")
GLM_GAM_results <- GLM_GAM_SRBC()
```